Sparse spectral and $p$-finite element methods for partial differential equations on disk slices and trapeziums

### 2019-11-19 papers/disk-slices-and-trapeziums/revised/halfdisk.tex
further edits to proof of lemma.

\begin{proof}
First, note that:
\begin{align}
	\genjacw^{(a,b,c) \: \prime}(x) &= - a \: \genjacw^{(a-1,b,c)}(x) + b \: \genjacw^{(a,b-1,c)}(x) + c \: \rho(x) \: \rho'(x) \:\genjacw^{(a,b,c-2)}(x), \label{eqn:derivativeofweightgenjac} \\
	\jacw^{(b) \: \prime}(y) &= - 2b \: y \: \jacw^{(b-1)}(y), \label{eqn:derivativeofweightjac} \\
	\rho(x) \: \rho'(x) &= -x. \label{eqn:rhoderivative}
\end{align}

@@

We next consider the case for the operator $D_x^{(a,b,c)}$ for partial differentiation by $x$. Since $\{\hdop^{(a+1, b+1, c+1)}_{m,j}\}$ for $m = 0,\dots,n-1$, $j = 0,\dots,m$ is an orthogonal basis for any degree $n-1$ polynomial, we can expand $\pddx \hdopnkabc = \sum_{m=0}^{n-1} \sum_{j=0}^m c_{m,j}^x \: \hdop^{(a+1, b+1, c+1)}_{m,j}$. The coefficients of the expansion are then the entries of the relevant operator matrix. As before, we can use an integration-by-parts argument to show that the only non-zero coefficients of this expansion are when $m = n-1, n-2, n-3$, $j = k, k-1, k-2$ and $0 \le j \le m$. First, note that
\begin{align*}
	c_{m,j}^x = {\ip<\pddx \hdopnkabc, \hdop^{(a+1, b+1, c+1)}_{m,j} >_{W^{(a+1, b+1, c+1)}}}{\norm{\hdop^{(a+1, b+1, c+1)}_{m,j}}^{-2}_{W^{(a+1, b+1, c+1)}}}.
\end{align*}
Now, again using the change of variable $t= \frac{y}{\rho(x)}$, and (\ref{eqn:rhoderivative}), we have that
\begin{align*}
	&\ip<\pddx \hdopnkabc, \hdop^{(a+1, b+1, c+1)}_{m,j} >_{W^{(a+1, b+1, c+1)}} \nonumber \\ 
	&= \Big( \int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1) \: \prime} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \rho^{k+j+1} \: \genjacw^{(a+1, b+1, 2c+2)} \: \D x \Big) \\
	&\quad \quad \quad \quad \quad \cdot \: \Big( \int_\gamma^\delta \jac_k^{(c,c)} \: \jac_j^{(c+1,c+1)} \: \jacw^{(c+1)} \: \D t \Big) \\ 
	& \quad + k \: \Big( \int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \rho^{k+j} \: \rho' \: \genjacw^{(a+1, b+1, 2c+2)} \: \D x \Big) \\
	& \quad \quad \quad \quad \quad \cdot \: \Big( \int_\gamma^\delta \jac_k^{(c,c)} \: \jac_j^{(c+1,c+1)} \: \jacw^{(c+1)} \: \D t \Big) \\
	& \quad - \Big( \int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \rho^{k+j} \: \rho' \: \genjacw^{(a+1, b+1, 2c+2)} \: \D x \Big) \\
	& \quad \quad \quad \quad \quad \cdot \: \Big( \int_\gamma^\delta t \: \jac_k^{(c,c) \: \prime} \: \jac_j^{(c+1,c+1)} \: \jacw^{(c+1)} \: \D t \Big). \\
\end{align*}
%\begin{align*}
%	&\ip<\pddx \hdopnkabc, \hdop^{(a+1, b+1, c+1)}_{m,j} >_{W^{(a+1, b+1, c+1)}} \nonumber \\ 
%	&= \normgenjac^{(a, b+\half)} \: \normjac^{(c+1)} \: \Big\{ \ip< \genjacnmk^{(a, b+k+\half) \: \prime} (x), \: \rho(x)^{k+j+2} \: \genjacmmj^{(a+1, b+1+j+\half)} >_{\genjacw^{(a, b+\half)}} \\ 
%	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \cdot \: \ip< \jac_k^{(b,b)}, \: \jac_j^{(b+1,b+1)} >_{\jacw^{(b+1)}}  \nonumber \\ 
%	& \quad - k \: \ip< x^2 \: \genjacnmk^{(a, b+k+\half)}(x), \: \rho(x)^{k+j} \: \genjacmmj^{(a+1, b+1+j+\half)} >_{\genjacw^{(a, b+\half)}} 
%		\: \ip< \jac_k^{(b,b)}, \: \jac_j^{(b+1,b+1)} >_{\jacw^{(b+1)}}  \nonumber \\ 
%	& \quad + \: \ip< x^2 \: \genjacnmk^{(a, b+k+\half)}(x), \: \rho(x)^{k+j} \: \genjacmmj^{(a+1, b+1+j+\half)} >_{\genjacw^{(a, b+\half)}} 
%		\: \ip< y \: \jac_k^{(b,b) \: \prime} (y), \: \jac_j^{(b+1,b+1)} >_{\jacw^{(b+1)}} \Big\}
%\end{align*}

We can see from each term's second factor that the above is only possibly non-zero for $j = k-2, k$. \bstodo{Need to give the working here!!}. Now, using (\ref{eqn:derivativeofweightgenjac}), integration-by-parts, and noting that the weight $\genjacw^{(a,b,2c)}$ is a polynomial degree $a+b+2c$ and vanishes at the limits of the integral for positive parameters $a,b,c$, we have that
\begin{align*}
	&\int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1) \: \prime} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \rho^{k+j+1} \: \genjacw^{(a+1, b+1, 2c+2)} \: \D x  \\
	&= \int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1) \: \prime} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \genjacw^{(a+1, b+1, 2c+k+j+3)} \: \D x \\
	&= - \int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1)} \: \ddx \Big[ \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \genjacw^{(a+1, b+1, 2c+k+j+3)} \Big] \: \D x \\
	&= - \int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1)} \: \Big\{ \genjacmmj^{(a+1, b+1, 2c+2j+3) \: \prime} \: \genjacw^{(a+1, b+1, 2c+k+j+3)} \\
	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad + (2c+k+j+3) \: \rho \: \rho' \:  \genjacw^{(a+1, b+1, 2c+k+j+1)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \\
	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad + (b+1) \: \genjacw^{(a+1, b, 2c+k+j+3)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \\
	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad - (a+1) \: \genjacw^{(a, b+1, 2c+k+j+3)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \Big\} \: \D x \\
	&= - \: \normgenjac^{(a, b, 2c+2k+1)} \:  \Big\{ \ip<\genjacnmk^{(a, b, 2c+2k+1)}, \: \genjacw^{(1, 1, j-k+2)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3) \: \prime}>_{\genjacw^{(a, b, 2c+2k+1)}} \\
		&\quad \quad \quad + (2c+k+j+3) \: \ip<\genjacnmk^{(a, b, 2c+2k+1)}, \: \rho \: \rho' \: \genjacw^{(1,1, j-k)} \genjacmmj^{(a+1, b+1, 2c+2j+3)} >_{\genjacw^{(a, b, 2c+2k+1)}} \\
		&\quad \quad \quad + (b+1) \: \ip<\genjacnmk^{(a, b, 2c+2k+1)}, \: \genjacw^{(1,0, j-k+2)} \genjacmmj^{(a+1, b+1, 2c+2j+3)} >_{\genjacw^{(a, b, 2c+2k+1)}} \\
		&\quad \quad \quad - (a+1) \: \ip<\genjacnmk^{(a, b, 2c+2k+1)}, \: \genjacw^{(0,1, j-k+2)} \genjacmmj^{(a+1, b+1, 2c+2j+3)} >_{\genjacw^{(a, b, 2c+2k+1)}} \Big\}
\end{align*}
By orthogonality, each term is is zero for $m-j+3+j-k < n-k \iff m < n - 3$ (since $j-k$ is even by the earlier argument and so $\text{deg}(\rho \: \rho' \: \genjacw^{(1,1, j-k)})$,  $\text{deg} (\genjacw^{(1,0, j-k+2)})$, $\text{deg} (\genjacw^{(0,1, j-k+2)}) = 3 + j-k$).

Finally,
\begin{align*}
	&\int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \rho^{k+j} \: \rho' \: \genjacw^{(a+1, b+1, 2c+2)} \: \D x \\
	&= \normgenjac^{(a, b, 2c+2k+1)} \: \ip< \genjacnmk^{(a, b, 2c+2k+1)}, \: \rho \: \rho' \: \genjacw^{(1, 1, j-k)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} >_{\genjacw^{(a, b, 2c+2k+1)}}
\end{align*}
which is also zero for $m < n - 3$.

@@

\begin{figure}[t]
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityoflaplacian-w11}
        \centering
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityofhelmholtz}
        \centering
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityofbiharmonic}
        \centering
	\end{subfigure}
    	\caption{"Spy" plots of (differential) operator matrices, showing their sparsity. Left: the Laplace operator $\laplacewiii$. Centre: the weighted variable coefficient Helmholtz operator $\laplacewiii + k^2 \: T^{(0,0,0)\to(1,1,1)} \: V({J_x^{(0,0,0)}}^\top, {J_y^{(0,0,0)}}^\top) \: T_W^{(1,1,1)\to(0,0,0)}$ for $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 200$. Right: the biharmonic operator $\biharmonictwo$.}
        \label{fig:sparsity}
        \centering
\end{figure}

@@

% FIGURES
\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.3]{solution-poisson}
	\centering
	%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.5]{solutionblocknorms-poisson}
        	%\label{fig:solutionblocknorms-poisson}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$. Right: The norms of each block of the computed solution of the Poisson equation with the given right hand side functions. This demonstrates algebraic convergence with the rate dictated by the decay at the corners, with spectral convergence observed when the right-hand side vanishes to all orders.}
	\centering
	\label{fig:poisson}
\end{figure}

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\centering
	\includegraphics[scale=0.3]{solution-helmholtz-k=100-n=1500}
	%\label{fig:solution-helmholtz}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[scale=0.5]{solutionblocknorms-helmholtz-k=20}
	\centering
        	%\label{fig:solutionblocknorms-helmholtz}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u + k^2 \: v \: u = f$ with zero boundary conditions with $f(x,y) = x(1-x^2-y^2)e^x$, $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 100$. Right: The norms of each block of the computed solution of the Helmholtz equation with the given right hand side functions, with $k=20$ and $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$.}
	\centering
	\label{fig:helmholtz}
\end{figure}

@@

>>>>

\begin{proof}
First, note that:
\begin{align}
	\genjacw^{(a,b,c) \: \prime}(x) &= - a \: \genjacw^{(a-1,b,c)}(x) + b \: \genjacw^{(a,b-1,c)}(x) + c \: \rho(x) \: \rho'(x) \:\genjacw^{(a,b,c-2)}(x), \label{eqn:derivativeofweightgenjac} \\
	\jacw^{(c) \: \prime}(y) &= - 2c \: y \: \jacw^{(b-1)}(y), \label{eqn:derivativeofweightjac} \\
	\rho(x) \: \rho'(x) &= -x. \label{eqn:rhoderivative}
\end{align}

@@

We next consider the case for the operator $D_x^{(a,b,c)}$ for partial differentiation by $x$. Since $\{\hdop^{(a+1, b+1, c+1)}_{m,j}\}$ for $m = 0,\dots,n-1$, $j = 0,\dots,m$ is an orthogonal basis for any degree $n-1$ polynomial, we can expand $\pddx \hdopnkabc = \sum_{m=0}^{n-1} \sum_{j=0}^m c_{m,j}^x \: \hdop^{(a+1, b+1, c+1)}_{m,j}$. The coefficients of the expansion are then the entries of the relevant operator matrix. As before, we can use an integration-by-parts argument to show that the only non-zero coefficients of this expansion are when $m = n-1, n-2, n-3$, $j = k, k-1, k-2$ and $0 \le j \le m$. First, note that
\begin{align*}
	c_{m,j}^x = {\ip<\pddx \hdopnkabc, \hdop^{(a+1, b+1, c+1)}_{m,j} >_{W^{(a+1, b+1, c+1)}}}{\norm{\hdop^{(a+1, b+1, c+1)}_{m,j}}^{-2}_{W^{(a+1, b+1, c+1)}}}.
\end{align*}
Now, again using the change of variable $t= \frac{y}{\rho(x)}$, we have that
\begin{align}
	&\ip<\pddx \hdopnkabc, \hdop^{(a+1, b+1, c+1)}_{m,j} >_{W^{(a+1, b+1, c+1)}} \nonumber \\ 
	&= \Big( \int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1) \: \prime} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \rho^{k+j+1} \: \genjacw^{(a+1, b+1, 2c+2)} \: \D x \Big) \nonumber \\
	&\quad \quad \quad \quad \quad \cdot \: \Big( \int_\gamma^\delta \jac_k^{(c,c)} \: \jac_j^{(c+1,c+1)} \: \jacw^{(c+1)} \: \D t \Big) \nonumber \\ 
	& \quad + k \: \Big( \int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \rho^{k+j} \: \rho' \: \genjacw^{(a+1, b+1, 2c+2)} \: \D x \Big) \nonumber \\
	& \quad \quad \quad \quad \quad \cdot \: \Big( \int_\gamma^\delta \jac_k^{(c,c)} \: \jac_j^{(c+1,c+1)} \: \jacw^{(c+1)} \: \D t \Big) \nonumber \\
	& \quad - \Big( \int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \rho^{k+j} \: \rho' \: \genjacw^{(a+1, b+1, 2c+2)} \: \D x \Big) \nonumber \\
	& \quad \quad \quad \quad \quad \cdot \: \Big( \int_\gamma^\delta t \: \jac_k^{(c,c) \: \prime} \: \jac_j^{(c+1,c+1)} \: \jacw^{(c+1)} \: \D t \Big). \label{eqn:dxsparsity}
\end{align}
We will first show that the second factor of each term in (\ref{eqn:dxsparsity}) are zero for $j < k - 2$ and also for $j = k - 1$. To this end, observe that, for any integer $c$, $\jac^{(c,c)}(-t) = (-1)^k \: \jac^{(c,c)}(t)$ and so $\jac_k^{(c,c)}$ is an even polynomial for even $k$, and an odd polynomial for odd $k$. Thus, $\jac_k^{(c,c)} \: \jac_{k-1}^{(c+1,c+1)}$ is an odd polynomial for any $k$. Hence
\begin{align*}
	\int_\gamma^\delta \jac_k^{(c,c)} \: \jac_j^{(c+1,c+1)} \: \jacw^{(c+1)} \: \D t = \int_{-\delta}^\delta \jac_k^{(c,c)} \: \jac_j^{(c+1,c+1)} \: \jacw^{(1)} \: \jacw^{(c)} \: \D t 
\end{align*}
is zero for $j < k - 2$ by orthogonality, and is zero for $j = k-1$ due to symmetry over the domain. Moreover, $t \: \jac_k^{(c,c) \: \prime}(t) \: \jac_j^{(c+1,c+1)}(t)$ is also an odd polynomial for any $k$ and so
\begin{align*}
	\int_\gamma^\delta t \: \jac_k^{(c,c) \: \prime}(t) \: \jac_j^{(c+1,c+1)}(t) \: \jacw^{(c+1)}(t) \: \D t
\end{align*}
is zero for $j = k-1$ due to symmetry over the domain, and
\begin{align*}
	&\int_\gamma^\delta t \: \jac_k^{(c,c) \: \prime} \: \jac_j^{(c+1,c+1)} \: \jacw^{(c+1)} \: \D t \\
	&= - \int_{-\delta}^\delta \jac_k^{(c,c)} \: \frac{\D}{\D t} \big[ t \: \jac_j^{(c+1,c+1)} \: \jacw^{(c+1)} \big] \: \D t \\
	&= - \int_{-\delta}^\delta \jac_k^{(c,c)} \: \big[ \jac_j^{(c+1,c+1)} \: \jacw^{(c+1)} + t \: \jac_j^{(c+1,c+1) \: \prime} \: \jacw^{(c+1)} - 2 c \: t^2 \: \jac_j^{(c+1,c+1)} \: \jacw^{(c)} \big] \: \D t \\
	&= - \: \normjac^{(c)} \: \ip< \jac_k^{(c,c)}, \: \jac_j^{(c+1,c+1)} \: \jacw^{(1)} + t \: \jac_{j}^{(c+1,c+1) \: \prime} \: \jacw^{(1)} - 2c \: t^2 \: \jac_{j}^{(c+1,c+1)}  >_{\jacw^{(c)}}
\end{align*}
which is zero for $j < k - 2$ by orthogonality. Thus, (\ref{eqn:dxsparsity}) is zero for $j \notin \{k-2, k\}$.

Now, using (\ref{eqn:derivativeofweightgenjac}), integration-by-parts, and noting that the weight $\genjacw^{(a,b,2c)}$ is a polynomial degree $a+b+2c$ and vanishes at the limits of the integral for positive parameters $a,b,c$, we have that
\begin{align}
	&\int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1) \: \prime} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \rho^{k+j+1} \: \genjacw^{(a+1, b+1, 2c+2)} \: \D x \nonumber  \\
	&= \int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1) \: \prime} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \genjacw^{(a+1, b+1, 2c+k+j+3)} \: \D x \nonumber \\
	&= - \int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1)} \: \ddx \Big[ \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \genjacw^{(a+1, b+1, 2c+k+j+3)} \Big] \: \D x \nonumber \\
	&= - \int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1)} \: \Big\{ \genjacmmj^{(a+1, b+1, 2c+2j+3) \: \prime} \: \genjacw^{(a+1, b+1, 2c+k+j+3)} \nonumber \\
	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad + (2c+k+j+3) \: \rho \: \rho' \:  \genjacw^{(a+1, b+1, 2c+k+j+1)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \nonumber \\
	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad + (b+1) \: \genjacw^{(a+1, b, 2c+k+j+3)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \nonumber \\
	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad - (a+1) \: \genjacw^{(a, b+1, 2c+k+j+3)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \Big\} \: \D x \nonumber \\
	&= - \: \normgenjac^{(a, b, 2c+2k+1)} \:  \Big\{ \ip<\genjacnmk^{(a, b, 2c+2k+1)}, \: \genjacw^{(1, 1, j-k+2)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3) \: \prime}>_{\genjacw^{(a, b, 2c+2k+1)}} \nonumber \\
		&\quad \quad \quad + (2c+k+j+3) \: \ip<\genjacnmk^{(a, b, 2c+2k+1)}, \: \rho \: \rho' \: \genjacw^{(1,1, j-k)} \genjacmmj^{(a+1, b+1, 2c+2j+3)} >_{\genjacw^{(a, b, 2c+2k+1)}} \nonumber \\
		&\quad \quad \quad + (b+1) \: \ip<\genjacnmk^{(a, b, 2c+2k+1)}, \: \genjacw^{(1,0, j-k+2)} \genjacmmj^{(a+1, b+1, 2c+2j+3)} >_{\genjacw^{(a, b, 2c+2k+1)}} \nonumber \\
		&\quad \quad \quad - (a+1) \: \ip<\genjacnmk^{(a, b, 2c+2k+1)}, \: \genjacw^{(0,1, j-k+2)} \genjacmmj^{(a+1, b+1, 2c+2j+3)} >_{\genjacw^{(a, b, 2c+2k+1)}} \Big\}. \label{eqn:dxsparsityR}
\end{align}
By recalling (\ref{eqn:rhoderivative}) and noting that $j-k$ is even by the earlier argument, we can see $\rho \: \rho' \: \genjacw^{(1,1, j-k)}$, $\genjacw^{(1,0, j-k+2)}$ and $\genjacw^{(1,0, j-k+2)}$ are all polynomials, and further that 
$$\text{deg}(\rho \: \rho' \: \genjacw^{(1,1, j-k)}) = \text{deg} (\genjacw^{(1,0, j-k+2)}) = \text{deg} (\genjacw^{(0,1, j-k+2)}) = 3 + j-k.$$ 
Hence, by orthogonality, each term in (\ref{eqn:dxsparsityR}) is is zero for $m-j+3+j-k < n-k \iff m < n - 3$.

Finally,
\begin{align*}
	&\int_\alpha^\beta \: \genjacnmk^{(a, b, 2c+2k+1)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} \: \rho^{k+j} \: \rho' \: \genjacw^{(a+1, b+1, 2c+2)} \: \D x \\
	&= \normgenjac^{(a, b, 2c+2k+1)} \: \ip< \genjacnmk^{(a, b, 2c+2k+1)}, \: \rho \: \rho' \: \genjacw^{(1, 1, j-k)} \: \genjacmmj^{(a+1, b+1, 2c+2j+3)} >_{\genjacw^{(a, b, 2c+2k+1)}}
\end{align*}
which is also zero for $m < n - 3$. Thus
\begin{align*}
	&\ip<\pddx \hdopnkabc, \hdop^{(a+1, b+1, c+1)}_{m,j} >_{W^{(a+1, b+1, c+1)}} = 0 \qfor m < n - 3, \: j \notin \{k-2, k\},
\end{align*}
showing that the only possible non-zero coefficients $c_{m,j}^x$ are when $m = n-3,\dots,n$ and $j = k-2,k$ $(j \le m)$.

@@

\begin{figure}[t]
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityoflaplacian-w11-diskslice-alpha=0p2-beta=0p8}
        \centering
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityofhelmholtz-diskslice-alpha=0p2-beta=0p8}
        \centering
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
	\includegraphics[scale=0.35]{sparsityofbiharmonic-diskslice-alpha=0p2-beta=0p8}
        \centering
	\end{subfigure}
    	\caption{"Spy" plots of (differential) operator matrices, showing their sparsity. Left: the Laplace operator $\laplacewiii$. Centre: the weighted variable coefficient Helmholtz operator $\laplacewiii + k^2 \: T^{(0,0,0)\to(1,1,1)} \: V({J_x^{(0,0,0)}}^\top, {J_y^{(0,0,0)}}^\top) \: T_W^{(1,1,1)\to(0,0,0)}$ for $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 200$. Right: the biharmonic operator $\biharmonictwo$.}
        \label{fig:sparsity}
        \centering
\end{figure}

@@

% FIGURES
\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.3]{solution-poisson}
	\centering
	%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.5]{solutionblocknorms-poisson-diskslice-alpha=0p2-beta=0p8}
        	%\label{fig:solutionblocknorms-poisson}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$. Right: The norms of each block of the computed solution of the Poisson equation with the given right hand side functions. This demonstrates algebraic convergence with the rate dictated by the decay at the corners, with spectral convergence observed when the right-hand side vanishes to all orders.}
	\centering
	\label{fig:poisson}
\end{figure}

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\centering
	\includegraphics[scale=0.3]{solution-helmholtz-k=100-n=1500}
	%\label{fig:solution-helmholtz}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[scale=0.5]{solutionblocknorms-helmholtz-diskslice-alpha=0p2-beta=0p8-N=196-k=20}
	\centering
        	%\label{fig:solutionblocknorms-helmholtz}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u + k^2 \: v \: u = f$ with zero boundary conditions with $f(x,y) = x(1-x^2-y^2)e^x$, $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$ and $k = 100$. Right: The norms of each block of the computed solution of the Helmholtz equation with the given right hand side functions, with $k=20$ and $v(x,y) = 1 - (3(x-1)^2 + 5y^2)$.}
	\centering
	\label{fig:helmholtz}
\end{figure}

@@

\begin{figure}[t]
	\begin{subfigure}{0.3\textwidth}
	\includegraphics[scale=0.3]{solution-poisson}
	\centering
	%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.5]{solutionblocknorms-poisson}
        	%\label{fig:solutionblocknorms-poisson}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y) = 1 + \text{erf}(5(1 - 10((x - 0.5)^2 + y^2)))$. Right: The norms of each block of the computed solution of the Poisson equation with the given right hand side functions. This demonstrates algebraic convergence with the rate dictated by the decay at the corners, with spectral convergence observed when the right-hand side vanishes to all orders.}
	\centering
	\label{fig:poisson}
\end{figure}
